{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-26 thesis/thesis.tex
turn off changebars
update acks

%\usepackage{fontspec}
\usepackage{mathspec}
\usepackage{xeCJK}
\usepackage[xetex]{xechangebar}
\usepackage[nomessages]{fp} % for xshearbox, see quicksand.tex

@@

\newcommand\revision[1]{#1\xspace}
%\newcommand\revision[1]{\cbstart[0.5em]{}#1\cbend\xspace}
\newcommand\revisionminor[1]{#1\xspace}
%\newcommand\revisionminor[1]{\cbstart{}#1\cbend\xspace}
% quicksand chapter revisions only
\newcommand\qrevision[1]{\cbstart[0.5em]{}#1\cbend\xspace}
\newcommand\qrevisionminor[1]{\cbstart{}#1\cbend\xspace}

@@

Ji\v{r}\'{i} \v{S}im\v{s}a, another former student of Garth's,
first sparked my interest in the field,
and then gave invaluable support during my first few years.
Ji\v{r}\'{i}'s mentorship
oriented me in the world of research and helped me find my bearings as a grad student,
from teaching me how DPOR works
to helping revise my paper drafts
to offering the kind of candid career advice you can't get from a professor.
Had I not met Ji\v{r}\'{i} and learned about dBug during grad school applications way back,
none of this would have happened.

{Many have collaborated with me directly on the research itself,
whom I thank here in approximate chapter order.
Michael J. Sullivan and Nathaniel Wesley Filardo were Landslide's first other users
%besides myself
back in its prototype days.
Joshua Wise, Miriam Zimmerman, and Glenn Willen helped revise my explanation of DPOR in \Cref{chap:landslide}.
Professor Brandon Lucia provided valuable revisions to \Cref{chap:quicksand}'s content
	that ultimately led to its publication at \mbox{OOPSLA}~2016.
Michael J. Sullivan double-checked the proofs therein.
Professor Timothy Zhu from Penn State University
and Professor Haryadi Gunawi and TA Kevin Zhao from the University of Chicago
graciously allowed me to use their students as guinea pigs
and helped to improve Landslide's
%stability and
robustness for use beyond CMU's walls,
greatly enriching \Cref{chap:education}'s evaluation.
David Blum and Skye Toor provided
invaluable advice towards the statistical analysis
used therein.
%that helped me evaluate the student
%grade distributions therein.
Mario Dehesa-Azuara generously contributed the transactional
% justify last line bc of manual page break
\unskip\parfillskip 0pt \par}

@@

%I am grateful to
The ThursDz Council,
my group of now-former grad student, Shadyside-bound (in spirit if not in person) restaurant-hoppers,
surrounded me with both friendship and mentorship over the years.
In particular,
%in alphabetical for lack of a better order,
Chris Martens,
Jason Reed,
Jim McCann,
Rob Simmons,
Tom 7,
and
William Lovas:
you each have been role models to me
perhaps more than you know.

@@

Looking back on my 11 years at CMU,
I am especially grateful for the friendships made early on %in my undergrad years
that continued well past first graduation.
From those who stayed in Pittsburgh %with me
to those who moved away but % can comment 'moved away but'
kept in touch,
from my regular tabletop, board, and/or dance gaming partners
to those who %inexhaustibly
welcomed me with company and
a couch to sleep on during travel,
I thank
%-- and in any order other than alphabetical here would be far too cruel --
8 Gianfortoni,
Adam Blank,
Alan Vangpat,
Alex Yuschik,
Anand Subramanian,
Andrew Krieger,
Car Bauer,
Carolyn Sawyer,
Elizabeth Kemp,
Elly Fong-Jones,
Emily Forney,
Emily Leathers,
Emma Cating-Subramanian,
Eric Faust,
Gabe Routh,
Greg Hanneman,
Hazel Vird\'{o},
Jack Ferris,
Jake Lengyel,
Jason Deng,
Josh Keller,
Joshua Wise,
Josiah Boning,
Julia Tuttle,
Kartik Subramanian,
Kellie ``K2'' Medlin,
Laura Abbott,
Maija Mednieks,
Margaret Meyerhofer,
Michael A\texttt{rntz}enius,
Michael J. ``Sully'' Sullivan,
Miriam Zimmerman,
Naomi Saphra,
Nathaniel Wesley Filardo,
Rhett Lauffenburger,
Richard Ha,
Rory Glenn,
Ryan Pearl,
and
Todd Eisenberger
for their wonderful friendship.
I am equally grateful to the new friends I made during my graduate years,
whether through board/card/dance gaming, tea drinking, %and/or
movie watching,
and/or as more permanent Pittsburgh residents that I am extremely torn up about moving away from:
%leaving behind (for now at least):
Alexandra Lee Falk,
Alexis Dyer,
Barbara Jensen,
Brendan McShane,
Brian Saghy,
Carlo Angiuli,
Cassie Orr,
Dan Guzek,
Danny Gratzer,
David Renshaw,
Evan Cavallo,
Gabriele Farina,
Grant Wu,
Jenny Lin,
Karl Schulz,
Kevin Nguyen,
Kristy Gardner,
Lea Albaugh,
Marlena Abraham,
Matt Stanec,
Matthew Maurer,
Sarah R. Allen,
Sol Boucher,
Stefan Muller,
Zachary Waldman,
Ziv Scully,
and the rest of ThursDz already named previously.
And to anyone who may read this list
and feel even slightly dejected that their name was left out:
I owe you a nice dinner. Get in touch.

@@

Lastly,
the Android: Netrunner community has become such an important part of my life
over the last half decade or so.
%for the better part of my time as a grad student.
Netrunner is a deckbuilding strategy card game
that depicts cyberspace hacking battles (completely different from real-life computer security)
alongside dystopian social issues (becoming strangely more familiar with each passing year).
Its characters have a diversity of ethnicity and gender identity %and sexual orientation
unparalleled in any other game I know of,
and the community that has grown around it reflects those values.
I thank especially the other Stimhack moderators,
%the members of
{\sf \#rainbow-coalition},
Nisei,
and the local Pittsburgh crew
for their support, encouragement,
and mutual exchange of inclusive ideals in these turbulent yet hopeful times.
%and
%friendships very real and deep, even when forged only in text,
%%\footnote{and Slack emojis},
%that will long outlive the silly card game that brought us together.
%%It'd be an injustice to list only a few names here and omit others, but you know who you are.
}

>>>>

%\usepackage{fontspec}
\usepackage{mathspec}
\usepackage{xeCJK}
%\usepackage[xetex]{xechangebar}
\usepackage[nomessages]{fp} % for xshearbox, see quicksand.tex

@@

\newcommand\revision[1]{#1\xspace}
%\newcommand\revision[1]{\cbstart[0.5em]{}#1\cbend\xspace}
\newcommand\revisionminor[1]{#1\xspace}
%\newcommand\revisionminor[1]{\cbstart{}#1\cbend\xspace}
% quicksand chapter revisions only
%\newcommand\qrevision[1]{\cbstart[0.5em]{}#1\cbend\xspace}
%\newcommand\qrevisionminor[1]{\cbstart{}#1\cbend\xspace}
\newcommand\qrevision[1]{#1\xspace}
\newcommand\qrevisionminor[1]{#1\xspace}

@@

Ji\v{r}\'{i} \v{S}im\v{s}a, another former student of Garth's,
%first sparked my interest in the field,
%and then
gave invaluable support during my first few years.
Ji\v{r}\'{i}'s mentorship
oriented me in the world of research,
%and helped me find my bearings as a grad student,
from teaching me how DPOR works
to helping revise my paper drafts
to offering the kind of candid career advice you can't get from a professor.
Had I not met Ji\v{r}\'{i} and learned about dBug during grad school applications way back,
none of this would have happened.

{Many have collaborated with me directly on the research itself,
whom I thank here in approximate chapter order.
Michael J. Sullivan and Nathaniel Wesley Filardo were Landslide's first other users
besides myself
back in its prototype days.
Joshua Wise, Miriam Zimmerman, and Glenn Willen helped revise my explanation of DPOR in \Cref{chap:landslide}.
Professor Brandon Lucia provided valuable revisions to \Cref{chap:quicksand}'s content
	that ultimately led to its publication at \mbox{OOPSLA}~2016.
Michael J. Sullivan double-checked the proofs therein.
Professor Timothy Zhu from Penn State University
and Professor Haryadi Gunawi and TA Kevin Zhao from the University of Chicago
graciously allowed me to use their students as guinea pigs
and helped to improve Landslide's
stability and
robustness for use beyond CMU's walls,
greatly enriching \Cref{chap:education}'s evaluation.
David Blum and Skye Toor provided
invaluable advice on statistical analysis
that helped me evaluate the student
grade distributions therein.
Mario Dehesa-Azuara generously contributed the transactional
% justify last line bc of manual page break
\unskip\parfillskip 0pt \par}

@@

%I am grateful to
The ThursDz Council,
my group of now-former grad student, Shadyside-bound (in spirit if not in person) restaurant-hoppers,
surrounded me with both friendship and mentorship over the years.
In particular,
%in alphabetical for lack of a better order,
Chris Martens,
jcreed,
Jim McCann,
Rob Simmons,
Tom 7,
and
William ``wjl'' Lovas:
you each have been role models to me
far more than you know.

@@

Looking back on my 11 years at CMU,
I am especially grateful for the early friendships %made early on %in my undergrad years
that continued well past first graduation.
From those who stayed in Pittsburgh %with me
to those who %moved away but % can comment 'moved away but'
kept in touch,
from regular tabletop, board, and/or dance gaming partners
to those who %inexhaustibly
%welcomed me with
offered
company and
a couch to sleep on while I traveled, %during travel,
I thank
%-- and in any order other than alphabetical here would be far too cruel --
8~Gianfortoni,
Adam Blank,
Alan Vangpat,
Alex Yuschik,
Anand Subramanian,
Andrew Krieger,
car bauer,
Carolyn Sawyer,
Elizabeth ``Kempy'' Kemp,
Elly Fong-Jones,
E.~Forney,
Emily~J Leathers,
Emma Cating-Subramanian,
Eric Faust,
Gabriel Mengde Routh,
Greg Hanneman,
hazel vird\'{o},
Jack Ferris,
Jake Lengyel,
Jason ``Wyrm'' Deng,
Joshua Keller,
Joshua Wise,
Josiah Boning,
Julia Tuttle,
Kartik Null Cating-Subramanian,
Kellie ``K2'' Medlin,
Laura Abbott,
Maija E. Mednieks,
Margaret Meyerhofer,
Michael A\texttt{rntz}enius,
Michael ``Sully'' Sullivan,
Miriam Zimmerman,
Naomi Saphra,
Nathaniel Wesley Filardo,
Rhett Lauffenburger,
Richard Ha,
rglenn,
Ryan Pearl,
Todd Eisenberger,
and
Zachary McCord
for their wonderful friendship.
I am equally grateful to the new friends I made during my graduate years,
whether through board/card/dance gaming, tea drinking, %and/or
movie watching,
and/or as more permanent Pittsburgh residents that I am extremely torn up about moving away from:
%leaving behind (for now at least):
Alexandra Lee Falk,
Alexis Dyer,
Barbara Jensen,
Brendan McShane,
Brian Saghy,
Carlo Angiuli,
Cassie Orr,
Charlie McGuffey,
Dan Guzek,
Danny Gratzer,
David Renshaw,
Evan Cavallo,
Gabriele Farina,
Grant Wu,
Isaac Grosof,
jennylin,
Karl Schulz,
Kevin Nguyen,
Kristy Gardner,
Lea Albaugh,
Marlena N. Abraham,
Matt Stanec,
Matthew Maurer,
Priya Donti,
Roie Levin,
Ryan Kavanagh,
Sarah R. Allen,
Sol Boucher,
Sophia Wu,
Stefan Muller,
Zachary Waldman,
Ziv Scully,
and the rest of ThursDz already named previously.
And to anyone who may read this list
and feel even slightly dejected that their name was left out:
I owe you a nice dinner. Get in touch.

@@

Lastly,
a shout out to the Android: Netrunner community.
%has become such an important part of my life
%over the last half decade or so.
%for the better part of my time as a grad student.
Netrunner is a deckbuilding strategy card game
that depicts cyberspace hacking battles (completely different from real-life computer security)
alongside dystopian social issues (becoming strangely more familiar with each passing year).
Its characters have a diversity of ethnicity and gender identity %and sexual orientation
unparalleled in any other game I know of,
and the community that has grown around it reflects those values.
I thank especially the other Stimhack moderators,
%the members of
{\sf \#rainbow-coalition},
Nisei,
and the local Pittsburgh crew
for their support, encouragement,
and mutual exchange of inclusive ideals in these turbulent yet hopeful times.
%and
%friendships very real and deep, even when forged only in text,
%%\footnote{and Slack emojis},
%that will long outlive the silly card game that brought us together.
%%It'd be an injustice to list only a few names here and omit others, but you know who you are.
}
